Understanding GDP Relations to Crime in US Cities

### 2017-03-08 resource/index.Rmd
pulling

>>>>

``` {r echo=FALSE}
linear.pop.gdp.crime <- lm(total_crime_rate_change_value ~ population_change_value + gdp_rate_change_value, data = linear.change.data)
summary(linear.pop.gdp.crime)

plot(lm(total_crime_rate_change_value ~ population_change_value, data = linear.change.data))

plot(lm(total_crime_rate_change_value ~ population_change_value, data = linear.change.data))
```
